Human capital mediates natural selection in contemporary humans

### 2022-05-14 why-natural-selection.Rmd
More colour tweaks

  my_shape_fill_guide <- guide_legend(order = 1)
  n_regs <- as.double(n_regs)
  shape_values <- c(16, 15, 17, 18, 20)[1:n_cats]
  if (fill_direction == -1) shape_values <- rev(shape_values)
  dfr %>% mutate(
    !! score_col := pretty_names(!! score_col),
    !! score_col := fct_reorder(!! score_col, estimate, order_abs(order_idx))
  ) %>% 
    rename(p = p.value) %>% 
    ggplot(aes(estimate, {{score_col}}, yend = {{score_col}}, 
               shape = {{fill_col}}, ...)) +
    my_vline + 
    confint_geom_segment +
    geom_point(size = 1.8, alpha = 0.9, aes(color = {{fill_col}})) +
    geom_point(size = 0.7, color = "white", aes(alpha = p < 0.05/{{n_regs}})) +
    my_fill_scale(aesthetics = "color", n = n_cats, direction = fill_direction, 
                    guide = my_shape_fill_guide) +
    scale_shape_manual(values = shape_values, guide = my_shape_fill_guide) +
    my_labs() +
    my_theme(legend.justification = "top") +
    confint_scale +
    scale_alpha_discrete(range = c(1, 0), 
                           guide = guide_legend(
                             order = 2,
                             override.aes = list(
                               shape = c(1, 16),
                               color = "black",
                               alpha = 1,
                               size = 1.8
                             )
                         )) 
}

@@

pval_geom_point <- function (size = 1.6, stroke = 0.9, fill = NULL, ...) {
  if (is.null(fill)) {
    geom_point(shape = 21, size = size, stroke = stroke, ...)
  } else {
    geom_point(shape = 21, size = size, stroke = stroke, fill = fill, ...)
  }
}

@@

  scale <- if (n <= 2) {
    dots <- list(...)
    dots$direction <- NULL
    do.call(scale_colour_manual, c(list(values = fill_colors[1:n],
                                        aesthetics = aesthetics), 
                                   dots))
  } else {
    # scale <- scale_color_viridis_d(aesthetics = aesthetics, option = "D",
    #                                  direction = direction, end = 0.6, ...)
    fill_colors <- c(fill_colors[1], "skyblue", fill_colors[2])
    if (direction != -1) fill_colors <- rev(fill_colors)
    scale_color_manual(aesthetics = aesthetics, 
                         values = shades::gradient(fill_colors,
                                                     steps = n, space = "Lab"), 
                         ...) 
  }

>>>>

  my_shape_fill_guide <- guide_legend(order = 1)

  n_regs <- as.double(n_regs)
  shape_values <- c(16, 15, 17, 18, 20)[1:n_cats]
  if (fill_direction == -1) shape_values <- rev(shape_values)
  dfr %>% mutate(
    !! score_col := pretty_names(!! score_col),
    !! score_col := fct_reorder(!! score_col, estimate, order_abs(order_idx))
  ) %>% 
    rename(p = p.value) %>% 
    ggplot(aes(estimate, {{score_col}}, yend = {{score_col}}, 
               shape = {{fill_col}}, ...)) +
    my_vline + 
    confint_geom_segment +
    geom_point(size = 1.8, alpha = 0.9, aes(color = {{fill_col}})) +
    geom_point(size = 0.7, color = "white", aes(alpha = p < 0.05/{{n_regs}})) +
    my_fill_scale(aesthetics = "color", n = n_cats, direction = fill_direction, 
                    guide = my_shape_fill_guide) +
    scale_shape_manual(values = shape_values, guide = my_shape_fill_guide) +
    my_labs() +
    my_theme(legend.justification = "top") +
    confint_scale +
    scale_alpha_discrete(range = c(1, 0), 
                           guide = guide_legend(
                             order = 2,
                             override.aes = list(
                               shape = c(1, 16),
                               color = "black",
                               alpha = 1,
                               size = 1.8
                             )
                         )) 
}

@@

@@

  scale <- if (n <= 2) {
    dots <- list(...)
    dots$direction <- NULL
    do.call(scale_colour_manual, c(list(values = fill_colors[1:n],
                                        aesthetics = aesthetics), 
                                   dots))
  } else {
    # scale <- scale_color_viridis_d(aesthetics = aesthetics, option = "D",
    #                                  direction = direction, end = 0.6, ...)
    fill_colors <- c(fill_colors[1], "#008b8b", fill_colors[2])
    if (direction != -1) fill_colors <- rev(fill_colors)
    scale_color_manual(aesthetics = aesthetics, 
                         values = shades::gradient(fill_colors,
                                                     steps = n, space = "Lab"), 
                         ...) 
  }
